Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-02-08 paper/main.tex
interpolated plot
metric per budget
arh and ari table
remove ode vs binomial section

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsmath,bm}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{cleveref}       % smart cross-referencing
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{bm}             % bold fonts for math symbols
\usepackage[misc]{ifsym}    % collection of symbols
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}          % force figure positioning in text
\usepackage{chngcntr}       % counters per section
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{comment}
\usepgfplotslibrary{dateplot, groupplots}
\pgfplotsset{compat=newest}
\usepackage{plotpolicies}   % custom package to plot policy-executions

@@

\subsection{Coping with stochastic transitions}

@@

To conduct this analysis, we evaluate our extension of PCN for continuous action-spaces on both the Binomial model. Conform to \citet{abrams2021modelling}, the simulation starts on the 1st of March 2020, by seeding a number of infections in the population. Two weeks later, on the 14th of March, the Belgian government initiated a full lockdown of the country. This is implemented by fixing the actions $p_w, p_s, p_l$ to $0.2, 0, 0.1$ respectively. This lockdown ended on the 4th of May 2020, at which point the government decided on a multi-phase exit strategy to incrementally reduce teleworking, reopen schools and allow leisure activities, such as the re-opening of bars and the cultural sector. It is from this day onward that PCN aims to learn policies for diverse exit strategies, compromising between the total number of daily new hospitalizations and the total number of contacts lost as a proxy for social burden. The simulation lasts throughout the school holidays (from 01/07/2020 to 31/08/2020). Schools are closed during the school holidays, which is simulated by setting $p_s = 0$, regardless of the corresponding value outputted by the policy, i.e., during periods of school closure $p_s$ is ignored.

@@

\begin{figure}
    \centering
    \input{fig/arh_binomial.tex}
    \caption{The Pareto front of policies discovered by PCN using the Binomial model, showing the different compromises between the number of hospitalizations and the number of lost contacts. As the budget increases, so does the coverage set learnt by PCN. Changes are most noticeable in the less restrictive trade-offs in terms of social burden.}
    \label{fig:pf-binomal-arh-budgets}
\end{figure}

@@

\subsection{ODE versus Binomial models}
\label{sec:ode-vs-binomial}

Next, we compare the performance of PCN when trained on the ODE and Binomial models. The ODE model has the advantage of using a deterministic transition function, for which PCN is suited. However, taking into account stochasticity, using the Binomial model, is important as individual behavioural changes introduce substantial uncertainty in the course of the outbreak and require stochastic model evaluations to evaluate the impact of this uncertainty on the effectiveness of the intervention strategies. Regardless, the results displayed in Table~\ref{tab:coverage-set} show that the solution sets that PCN finds using the Binomial model are competitive with the ODE model, as indicated by their hypervolumes and $I_{\varepsilon-mean}$ metrics. We do note that the difference in $I_{\varepsilon}$ indicator is more significant, indicating that a few solutions discovered using the ODE model are not found when using the Binomial model, impacting worst-case performance. Overall, we see that our extension of PCN performs efficiently, even with some degree of stochasticity in the transition function.

\begin{table}[t]
  \centering
  \setlength{\tabcolsep}{0.5em} % for the horizontal padding
  {\renewcommand{\arraystretch}{1.2}% for the vertical padding
  \input{tab_coverage-set}
  }
  \caption{Evaluation metrics for the coverage sets comparing hospitalizations with social burden. In general training on the ODE results in slightly better coverage sets than on the Binomial model. Training on infections (ARI) still provides a competitive coverage set in terms of hospitalizations. All PCN coverage sets outperform the baseline.}
  \label{tab:coverage-set}
\end{table}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsmath,bm}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{cleveref}       % smart cross-referencing
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{bm}             % bold fonts for math symbols
\usepackage[misc]{ifsym}    % collection of symbols
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}          % force figure positioning in text
\usepackage{chngcntr}       % counters per section
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{comment}
\usepgfplotslibrary{dateplot, groupplots, fillbetween}
\pgfplotsset{compat=newest}
\usepackage{plotpolicies}   % custom package to plot policy-executions

@@

\subsection{Coping with stochastic transitions}
\label{sec:pcn-stochastic}

@@

To conduct this analysis, we evaluate our extension of PCN for continuous action-spaces on both the Binomial model. \todo{reason for binomial}. As explained in Section~\ref{sec:pcn-stochastic}, we extend PCN for environments with stochastic transitions. While all results in this Section concern the Binomial model, we observe similar performance on the ODE model, showing that our extension does resolve the stochasticity issue. These results are available in the SI.

Conform to \citet{abrams2021modelling}, the simulation starts on the 1st of March 2020, by seeding a number of infections in the population. Two weeks later, on the 14th of March, the Belgian government initiated a full lockdown of the country. This is implemented by fixing the actions $p_w, p_s, p_l$ to $0.2, 0, 0.1$ respectively. This lockdown ended on the 4th of May 2020, at which point the government decided on a multi-phase exit strategy to incrementally reduce teleworking, reopen schools and allow leisure activities, such as the re-opening of bars and the cultural sector. It is from this day onward that PCN aims to learn policies for diverse exit strategies, compromising between the total number of daily new hospitalizations and the total number of contacts lost as a proxy for social burden. The simulation lasts throughout the school holidays (from 01/07/2020 to 31/08/2020). Schools are closed during the school holidays, which is simulated by setting $p_s = 0$, regardless of the corresponding value outputted by the policy, i.e., during periods of school closure $p_s$ is ignored.

@@

\begin{figure}
    \centering
    \input{fig/arh_binomial_both}
    \caption{The Pareto front of policies discovered by PCN using the Binomial model, showing the different compromises between the number of hospitalizations and the number of lost contacts. As the budget increases, so does the coverage set learnt by PCN. Changes are most noticeable in the less restrictive trade-offs in terms of social burden.}
    \label{fig:pf-binomal-arh-budgets}
\end{figure}

@@

\begin{table}[t]
  \centering
  \setlength{\tabcolsep}{0.5em} % for the horizontal padding
  {\renewcommand{\arraystretch}{1.2}% for the vertical padding
  \input{tab/arh/binomial}
  }
  \caption{Evaluation metrics for the coverage sets comparing hospitalizations with social burden. In general training on the ODE results in slightly better coverage sets than on the Binomial model. Training on infections (ARI) still provides a competitive coverage set in terms of hospitalizations. All PCN coverage sets outperform the baseline.}
  \label{tab:coverage-set}
\end{table}
